The \dealii Library, Version 9.7

### 2025-07-08 9.7/paper.tex
We are at version 9.7
Add question for modules

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii, version 9.8.
\end{abstract}

@@

>>>>

\begin{abstract}
  This paper provides an overview of the new features of the finite element
  library \dealii, version 9.7.
\end{abstract}

@@

\todo[inline]{Given that we haven't merged CMake support, the deal.II module isn't usable yet. Should we still include a discussion here?}
